---
title: "MechanaCarChallenge"
author: 'by: Valeria Achoa'
---
```{r}
library("tidyverse") #import tidyverse package
library("readr")
```


```{r}
mechaCarData <- read_csv("Resources/MechaCar_mpg.csv") #import MechaCar data
head(mechaCarData) #display first rows of imported data
```

## Deliverable 1  - Linear Regression to Predict MPG

### Perform linear regression using the lm() function on 6 variables: vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance
```{r}
lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance,data=mechaCarData) 
```
### Generate Summary Statistics
```{r}
summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance,data=mechaCarData)) 

```
## Deliverable 2: Create Visualizations for the Trip Analysis

```{r}
suspension_coil_data <- read_csv("Resources/Suspension_Coil.csv") #import suspension coil data
head(suspension_coil_data)
```

### Part2 - Table1 - Table of Total Summary : Mean, Median, Variance, SD
```{r}
total_summary <- suspension_coil_data %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI),SD=sd(PSI), .groups = 'keep') #create total summary table
total_summary
```

### Part2 - Table2 - Table of Summary of the lots: Mean, Median, Variance, SD
```{r}
lot_summary <- suspension_coil_data %>% group_by(Manufacturing_Lot) %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI),SD=sd(PSI), .groups = 'keep') #create lot summary table
lot_summary

```
### Part2 - Plot 1 -Plot all data (PSI) vs. density

```{r}
plt <- ggplot(suspension_coil_data,aes(x=PSI)) #import all coil data into ggplot2
plt + geom_density() #visualize distribution with density plot
```

### Part2 - Plot 1 - Plot sample (n=50) (log PSI) vs. density

```{r}
global_sample_table <- suspension_coil_data %>% sample_n(50) 
#randomly sample 50 data points
# plot sample data with a log scale log10(PSI) vs. density
plt <- ggplot(global_sample_table,aes(x=log10(PSI))) #import sample coil data into ggplot2
plt + geom_density() #visualize distribution with density plot
```
## Deliverable 3: T-Tests on Suspension Coils 

### Part3 - t-test of the Sample versus Population Mean
```{r}
t.test(global_sample_table$PSI,mu=mean(suspension_coil_data$PSI)) #compare sample versus population mean
```



### Part 3 - PSI - LOT 1 sample
```{r}
psi_lot1_sample <- suspension_coil_data %>% subset(Manufacturing_Lot=='Lot1') %>% sample_n(25) #create a sample table of 25 data points with Lot 1
t.test(psi_lot1_sample$PSI,mu=mean(suspension_coil_data$PSI)) #compare Lot1 sample versus population mean
```
### Part 3 - PSI - LOT 2 sample
```{r}
psi_lot2_sample <- suspension_coil_data %>% subset(Manufacturing_Lot=='Lot2') %>% sample_n(25) #create a sample table of 25 data points with Lot 2
t.test(psi_lot2_sample$PSI,mu=mean(suspension_coil_data$PSI)) #compare Lot2 sample versus population mean
```
### PSI - LOT 3 sample
```{r}
psi_lot3_sample <- suspension_coil_data %>% subset(Manufacturing_Lot=='Lot3') %>% sample_n(25) #create a sample table of 25 data points with Lot 3
t.test(psi_lot3_sample$PSI,mu=mean(suspension_coil_data$PSI)) #compare Lot3 sample versus population mean
```

