---
title: "MechanaCarChallenge"
author: "Valeria Achoa"
output: html_notebook
---
```{r}
library("dplyr") #import dplyr package
mechaCarData <- read_csv("Resources/MechaCar_mpg.csv") #import MechaCar data
head(mechaCarData) #display first rows of imported data
```
## Deliverable 1  - 
#### Perform linear regression using the lm() function on 6 variables: vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance
```{r}
lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance,data=mechaCarData) 
```
### Generate Summary Statistics
```{r}
summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + AWD + ground_clearance,data=mechaCarData)) 

```
## Deliverable 2: Create Visualizations for the Trip Analysis
```{r}
suspension_coil_data <- read_csv("Resources/Suspension_Coil.csv") #import suspension coil data
head(suspension_coil_data)
```
#### Table of Total Summary : Mean, Median, Variance, SD
```{r}
total_summary <- suspension_coil_data %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI),SD=sd(PSI), .groups = 'keep') #create total summary table
total_summary
```
### Table of Summary of the lots: Mean, Median, Variance, SD
```{r}
lot_summary <- suspension_coil_data %>% group_by(Manufacturing_Lot) %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI),SD=sd(PSI), .groups = 'keep') #create lot summary table
lot_summary

```
### Plot all data (PSI) vs. density

```{r}
plt <- ggplot(suspension_coil_data,aes(x=PSI)) #import all coil data into ggplot2
plt + geom_density() #visualize distribution with density plot
```

### Sample of 50 lots and plot with a log10 scale PSI vs. density

```{r}
global_sample_table <- suspension_coil_data %>% sample_n(50) 
#randomly sample 50 data points
# plot sample data with a log scale log10(PSI) vs. density
plt <- ggplot(global_sample_table,aes(x=log10(PSI))) #import sample coil data into ggplot2
plt + geom_density() #visualize distribution with density plot
```

